Expected Dependency Pair Match: Predicting translation quality with expected syntactic structure

### 2009-08-11 reviewers/review-response.tex

\item p.7 ``Score combination'' --- see comment above 
  \begin{response}
    As mentioned above, this was reduced to one line.
  \end{response}

\item ``Tuned, like the ...''  --- ungrammatical sentence?
  \begin{response}
    Clarified.
  \end{response}

\item  Evaluation (p. 8) In principle I like the idea of teasing apart
  sentence difficulty and translation quality. However, I have two
  reservations: (1), you are losing comparability of scores across
  sentences; and (2), you are committing to a scenario where you
  always have access to a sufficient number of translations in order
  to estimate the mean score. In other words, in the limit of one
  system, you do not predict anything.  These issues should be
  mentioned and discussed.  
  \begin{response}
    This method is used for evaluating the evaluation metric, not for
    evaluation itself, so comparability of scores across sentences is
    not really an issue for us.  That said, we agree that mean 
    normalization is not possible in all
    scenarios and in fact did not use it in section four.  Hence, we
    moved the mean normalization description to section 5, since it
    is only used when we have multiple translations.  
  \end{response}
  (Note about presentation: you don't
  introduce the variable $t$ in Equation 3 -- I guess this is the
  segment?)
  \begin{response}
    Fixed, but to save space the equation is now inline and not numbered.
  \end{response}

  More generally, I would like to see a motivation for the evaluation
  you perform. You seem to largely follow Owczarzak et al's
  evaluation, e.g. in the choice of data (Section 4.1), but you depart
  from it in some crucial respects (e.g. the definition of the
  dependent variable by mean subtraction). Can you provide a clearer
  description of why each experiment is set up in the way it is?
  \begin{response}
    Section 4 is intended to match the Owczarzak \textit{et al.} paradigm
    as closely as possible, but sections 5 and 6 do not since the focus 
    is on HTER. As mentioned above, mean subtraction is {\bf not} used 
    in section 4 and discussion of that was moved for clarity.  We think
    that this concern is really a lack of clarity in the original submission
    which has hopefully now been fixed.

    In addition, we move the detailed list of decompositions explored
    from section 3 to section 4, since section 4 explores
    decompositions --- later sections use fixed (s.~5) and
    greatly-reduced (s.~6) sets of decompositions, so the detailed
    list fits more succinctly and appropriately in section 4 alone.
  \end{response}

### 2009-08-11 reviewers/review-response.tex

\item  p.3, ``In section 2 etc.'' I'm not sure that a 12-page paper
  requires a table of contents.
  \begin{response}
    This paragraph has also been compressed.
  \end{response}

\item  p.3, reference to Owczarzak et al.'s work. In particular since
  their work has also appeared in the MT journal (please update the
  reference, btw!), it would be good to expand on the similarities and
  differences of your work and theirs.
  \begin{response}
    Both references are cited in the introduction.  In the comparative
    discussions, the earlier reference is cited since we were not aware of
    the MT journal paper when doing the work and experiments were designed
    with the first paper in mind.  We feel that our paper did have 
    discussion of the similarities and differences, but with the compression
    of other material these are better highlighted in the revisions. In addition, the last
    paragraph of section 1 now states that section 4 is in part aimed at making
    the comparison.
  \end{response}

\item p.4 I'm not so sure that I believe in the benefit of overweighting.
  In standard dependency graphs, for example, modifications are
  usually dependendents of the head and are thus ``underweighted'' by
  your scheme, but modifiers like negations etc. can considerably
  change the meaning.  (You write ``we argue'' but I don't see an
  argument, just a claim -- details of counts for an example might be
  helpful.)
  \begin{response}
  We have added a sentence at the end of the paragraph pointing to the example
to motivate the ``overweighting''. (now 1st paragraph on page 4)
  \end{response}

\item p.5 ``When multiple decompositions etc.'' As far as I can see, you
  get consistently better scores for F[] than for $\mu_{PR}[]$
  throughout your experiments.  I'd suggest reducing the discussion of
  $\mu$ here and in Section 3.2 with a short explanation that $\mu$
  has been found to work worse than F.
  \begin{response}
  We have compressed the discussion somewhat in section 2,
  substantially in section 3 (to a single line, now in section 4), and combined the original Tables I and II without the $\mu$ results, and then mention $\mu$ findings in a sentence of the text. Since
this finding is significant and provides insight into differences between other methods in terms of score combination, we did not want to eliminate it entirely.
  \end{response}

### 2009-08-11 mtjournal.tex
missing paradigm section label
grammar fixups at last minute

Alternative measures that 
incorporate synonym knowledge sources include: METEOR
\cite{banerjee05meteor}, which uses synonym tables and
morphological stemming to do progressively more forgiving matching;
%%MO: I am taking out the tuning stuff here since it isn't critical
%It can be tuned towards recall or precision, but is generally not
%tuned by users.  
TER Plus (TERp) \cite{snover09terp}, which is an extension of the
previously-mentioned TER that also incorporates synonym sets and stemming, along
with automatically-derived paraphrase tables.  
%TERp is explicitly
%intended to be tuned to a development set by users.
%
%Tuning has the advantage that the weight of different types of errors
%can be adjusted to match the needs of the task, though it makes it
%more difficult to compare results across tasks, particularly when
%there is little data for tuning.
Other metrics model syntactically-local (rather than string-local)
word-sequences include: tree-local
$n$-gram precision in various configurations of constituency and
dependency trees \cite{liu05syntaxformteval};
%%MO: Since sparseval is cited elsewhere, I don't think we need the endnote
%\endnote{The dependency-based SParseval measure
%\cite{roark06:sparseval}, designed as a parse-quality metric for
%speech, is a similar approach, in that it is an F-measure over a
%decomposition of reference and hypothesis trees.} 
and the \textbf{d} and
\textbf{d\_var} measures proposed by \inlinecite{owczarzak07evaluatingmt}
%%MO: This is a hack to get the second year without the name
(2007b) 
that compare relational tuples derived from a
lexical functional grammar (LFG)
over reference and hypothesis translations.\endnote{
  \inlinecite{owczarzak07evaluatingmt} extend their previous line of
  research \cite{owczarzak07labelleddepseval}  by variably-weighting
%%MO: you actually do variable weighting using parse probabilities, so
%% would be good to mention what they use.  If you can say this in a few
%% words, then you won't add a line
  dependencies and by including synonym matching, two directions not
  pursued here. Hence, the earlier paper is cited in comparisons.
}
%
These syntactically-oriented measures require a system for proposing
dependency structure over the reference and hypothesis
translations. \inlinecite{liu05syntaxformteval} use a
PCFG parser with deterministic head-finding, while 
\cite{owczarzak07evaluatingmt} extract the semantic dependency
relations from an LFG parser \cite{cahill04lfg}.
%
This work extends the dependency-scoring strategies of
\inlinecite{owczarzak07evaluatingmt}, which reported substantial
improvement in correlation with human judgment relative to BLEU and
TER, by using a 
publicly-available probabilistic context-free grammar (PCFG) parser and deterministic head-finding rules. In addition, we consider more types of constituents and different score combinations, as well as combination with of synonym-type scores.

@@

\section{Parsing and dependency extraction}

@@

We explore various configurations of the DPM by assessing the results
against a corpus of human judgments of fluency and adequacy,
specifically the LDC Multiple Translation Chinese corpus parts
2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}, which are composed of
translations of written Chinese news stories.  These corpora include
multiple human judgments of fluency and adequacy for each sentence
(assigned on a five-point scale), with each judgment using a different
human judge and a different reference translation.  For a
rough\endnote{Our segment count differs slightly from
  \inlinecite{owczarzak07evaluatingmt}
  for the same corpus: 16,807 vs.\ 16,815. 
  As a result, the baseline 
  per-segment correlations differ slightly (BLEU$_4$ is higher here,
  while TER here is lower), but the trends in gains over those
  baselines are very similar.  } comparison with
\inlinecite{owczarzak07evaluatingmt}, we treat each judgment as a
separate segment, which yields 16,815 tuples of $\langle$hypothesis,
reference, fluency, adequacy$\rangle$.  We compute the per-segment
correlations\endnote{The use of the same hypothesis translations in
  multiple comparisons in the Multiple Translation Corpus means that
  scored segments are not strictly independent, but for methodological
  comparison with prior work, this strategy is preserved.}
%
The baselines for comparison are case-sensitive BLEU (4-grams, with add-one smoothing) and TER.

@@

\section{Correlating EDPM with HTER}
\label{sec:hter1}
In this section, we compare EDPM to baseline metrics in terms of
document- and segment-level correlation with HTER scores using the
GALE 2.5 translation corpus.  The corpus includes system translations
into English from three sites, all of which use system combination to
integrate results from several systems, some phrase-based and some
that use syntax on either the source or target side. No system
provided system-generated parses.
%
The source data comprises Arabic and Chinese in four
genres: \texttt{bc} (broadcast conversation), \texttt{bn} (broadcast
news), \texttt{nw} (newswire), and \texttt{wb} (web text), with corpus
sizes shown in table~\ref{tab:galestats}.
The corpus includes one English reference translation
\cite{gale08phase2_5references} for each sentence and a system
translation for each of the three systems. Additionally,
each of the system translations has a
corresponding human-targeted reference aligned at the sentence level,
and an associated so we have available the HTER score at
both the sentence and document level.

>>>>

Alternative measures that 
incorporate synonym knowledge sources include: METEOR
\cite{banerjee05meteor}, which uses synonym tables and
morphological stemming to do progressively more forgiving matching;
%%MO: I am taking out the tuning stuff here since it isn't critical
%It can be tuned towards recall or precision, but is generally not
%tuned by users.  
TER Plus (TERp) \cite{snover09terp}, which is an extension of the
previously-mentioned TER that also incorporates synonym sets and stemming, along
with automatically-derived paraphrase tables.  
%TERp is explicitly
%intended to be tuned to a development set by users.
%
%Tuning has the advantage that the weight of different types of errors
%can be adjusted to match the needs of the task, though it makes it
%more difficult to compare results across tasks, particularly when
%there is little data for tuning.
Other metrics modeling syntactically-local (rather than string-local)
word-sequences include: tree-local
$n$-gram precision in various configurations of constituency and
dependency trees \cite{liu05syntaxformteval};
%%MO: Since sparseval is cited elsewhere, I don't think we need the endnote
%\endnote{The dependency-based SParseval measure
%\cite{roark06:sparseval}, designed as a parse-quality metric for
%speech, is a similar approach, in that it is an F-measure over a
%decomposition of reference and hypothesis trees.} 
and the \textbf{d} and
\textbf{d\_var} measures proposed by \inlinecite{owczarzak07evaluatingmt}
%%MO: This is a hack to get the second year without the name
(2007b) 
that compare relational tuples derived from a
lexical functional grammar (LFG)
over reference and hypothesis translations.\endnote{
  \inlinecite{owczarzak07evaluatingmt} extend their previous line of
  research \cite{owczarzak07labelleddepseval}  by variably-weighting
%%MO: you actually do variable weighting using parse probabilities, so
%% would be good to mention what they use.  If you can say this in a few
%% words, then you won't add a line
  dependencies and by including synonym matching, two directions not
  pursued here. Hence, the earlier paper is cited in comparisons.
}
%
These syntactically-oriented measures require a system for proposing
dependency structure over the reference and hypothesis
translations. \inlinecite{liu05syntaxformteval} use a
PCFG parser with deterministic head-finding, while 
\cite{owczarzak07evaluatingmt} extract the semantic dependency
relations from an LFG parser \cite{cahill04lfg}.
%
This work extends the dependency-scoring strategies of
\inlinecite{owczarzak07evaluatingmt}, which reported substantial
improvement in correlation with human judgment relative to BLEU and
TER, by using a 
publicly-available probabilistic context-free grammar (PCFG) parser and deterministic head-finding rules. In addition, we consider more types of constituents and different score combinations, as well as combination with of synonym-type scores.

@@

\section{Parsing and dependency extraction}
\label{sec:paradigm}

@@

We explore various configurations of the DPM by assessing the results
against a corpus of human judgments of fluency and adequacy,
specifically the LDC Multiple Translation Chinese corpus parts
2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}, which are composed of
translations of written Chinese news stories.  These corpora include
multiple human judgments of fluency and adequacy for each sentence
(assigned on a five-point scale), with each judgment using a different
human judge and a different reference translation.  For a
rough\endnote{Our segment count differs slightly from
  \inlinecite{owczarzak07evaluatingmt}
  for the same corpus: 16,807 vs.\ 16,815. 
  As a result, the baseline 
  per-segment correlations differ slightly (BLEU$_4$ is higher here,
  while TER here is lower), but the trends in gains over those
  baselines are very similar.  } comparison with
\inlinecite{owczarzak07evaluatingmt}, we treat each judgment as a
separate segment, which yields 16,815 tuples of $\langle$hypothesis,
reference, fluency, adequacy$\rangle$.  We compute per-segment
correlations.\endnote{The use of the same hypothesis translations in
  multiple comparisons in the Multiple Translation Corpus means that
  scored segments are not strictly independent, but for methodological
  comparison with prior work, this strategy is preserved.}
%
The baselines for comparison are case-sensitive BLEU (4-grams, with add-one smoothing) and TER.

@@

\section{Correlating EDPM with HTER}
\label{sec:hter1}
In this section, we compare EDPM to baseline metrics in terms of
document- and segment-level correlation with HTER scores using the
GALE 2.5 translation corpus.  The corpus includes system translations
into English from three sites, all of which use system combination to
integrate results from several systems, some phrase-based and some
that use syntax on either the source or target side. No system
provided system-generated parses.
%
The source data comprises Arabic and Chinese in four
genres: \texttt{bc} (broadcast conversation), \texttt{bn} (broadcast
news), \texttt{nw} (newswire), and \texttt{wb} (web text), with corpus
sizes shown in table~\ref{tab:galestats}.
The corpus includes one English reference translation
\cite{gale08phase2_5references} for each sentence and a system
translation for each of the three systems. Additionally,
each of the system translations has a
corresponding human-targeted reference aligned at the sentence level,
so we have available the HTER score at
both the sentence and document level.
